High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-09 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

% Abstract of the paper
\begin{abstract}
    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimeter Array (ALMA).    We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm radio continuum. These observations, combined with SPHERE-IRDIS polarized scattered light images, allow us to characterize the disc structure.  We reproduce the available observations, including the spectral energy distribution, in terms of a physical structure using a parametric radiative transfer (RT) model.  We report a two-ringed structure for the 1.3 mm dust emission with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.  The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au.  We deproject the images in polar coordinates to better constrain the disc radial structure.  The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.   The model predicts a three-ringed structure for the small-dust population with an inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.  The shadow of the secondary star reported previously from scattered-light data is also reproduced by our RT model. The polarized light image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains. Using the parametric model scale-height as an estimated height, we found that the thin inner ring is stable. Deeper ALMA observations may confirm the lopsided 6\,au ring.
\end{abstract}

@@

Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources. ***EXPAND, I would give a general description on substructures and cite ``e.g. Andrews (2020) for a recent review''***

>>>>

% Abstract of the paper
\begin{abstract}
    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimetre Array (ALMA). We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm radio continuum. These observations, combined with SPHERE-IRDIS polarized scattered light images, allow us to characterize the disc structure. We reproduce the available observations, including the spectral energy distribution, in terms of a physical structure using a parametric radiative transfer (RT) model. We report a two-ringed structure for the 1.3 mm dust emission with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au. The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au. We deproject the images in polar coordinates to better constrain the disc radial structure. The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au. The model predicts a three-ringed structure for the small-dust population with an inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations. The shadow of the secondary star reported previously from scattered-light data is also reproduced by our RT model. The polarized light image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains. Using the parametric model scale-height as an estimated height, we found that the thin inner ring is stable. Deeper ALMA observations may confirm the lopsided 6\,au ring.
\end{abstract}

@@

Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources. ***EXPAND, I would give a general description on substructures and cite ``e.g. Andrews (2020) for a recent review''***
